Supporting information for\\ \emph{Effectiveness of UNAIDS targets and HIV vaccination across 127 countries}

### 2017-03-07 docs/supporting_information.tex
Fixed label for new region names.

Transitions between model states are governed by a system of
differential equations parametrized using values found in other
studies, along with transmission rates derived from UNAIDS estimates
of incidence and prevalence (\autoref{model_param}).  The model is
deterministic, but uncertainty in the parameters was treated by
running the model 1000 times with samples from the parameter
distributions (\autoref{uncertainty}) and summarizing the model
outcomes using the median and percentiles.  Each country was modeled
separately
(\hyperref[effectiveness_Afghanistan]{Figs.~\ref*{effectiveness_Afghanistan}}--\ref{effectiveness_Zimbabwe})
and the country simulations were aggregated to calculate global and
regional outcomes
(\hyperref[effectiveness_Global]{Figs.~\ref*{effectiveness_Global}}--\ref*{effectiveness_Western_Europe}).

>>>>

Transitions between model states are governed by a system of
differential equations parametrized using values found in other
studies, along with transmission rates derived from UNAIDS estimates
of incidence and prevalence (\autoref{model_param}).  The model is
deterministic, but uncertainty in the parameters was treated by
running the model 1000 times with samples from the parameter
distributions (\autoref{uncertainty}) and summarizing the model
outcomes using the median and percentiles.  Each country was modeled
separately
(\hyperref[effectiveness_Afghanistan]{Figs.~\ref*{effectiveness_Afghanistan}}--\ref{effectiveness_Zimbabwe})
and the country simulations were aggregated to calculate global and
regional outcomes
(\hyperref[effectiveness_Global]{Figs.~\ref*{effectiveness_Global}}--\ref*{effectiveness_Western_and_Central_Europe}).
